### 2018-09-17 sections/signal_background_modeling.tex
jason comments and fix to prelim plot

Signal and most background processes are modelled using Monte Carlo (MC) simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multijet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e. those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is allowed to decay into all SM particles with branching ratios calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\tauhad$ candidates, 
generically referred to as ``fake leptons", are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Hbb} and~\ref{sec:strategy_Htautau}.

@@

The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template") derived from data in the corresponding CR. The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates, originating primarily from 
$W(\to \tau\nu)$+jets and $Z(\to \tau\tau)$+jets, are subtracted. In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$. In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production. However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\tauhad$ background is higher in the SR than in the CR. Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR is added to the fake $\tauhad$ template to match the fake $\tauhad$ background composition in the SR. 
In both the $\lephad$ and $\hadhad$ channels, the fake $\tauhad$ template in each SR is initially normalised to the estimated fake $\tauhad$ background yield, 
defined as the data yield minus the contributions from the simulated backgrounds with real $\tauhad$ candidates (i.e. assuming no signal contribution).
During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR will be allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.

>>>>

Signal and most background processes are modelled using Monte Carlo (MC) simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multijet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e. those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is allowed to decay into all SM particles with branching ratios calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\tauhad$ candidates, 
generically referred to as ``fake leptons'', are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Hbb} and~\ref{sec:strategy_Htautau}.

@@

The fake $\tauhad$ background prediction in a given SR is modelled by the distribution (referred to as ``fake $\tauhad$ template'') derived from data in the corresponding CR. The fake $\tauhad$ template is defined as the data distribution from which the contributions from the simulated backgrounds with real $\tauhad$ candidates, originating primarily from 
$W(\to \tau\nu)$+jets and $Z(\to \tau\tau)$+jets, are subtracted. In the $\lephad$ channel, simulation studies indicate that the fake $\tauhad$ background composition is consistent between the SR and the CR, and dominated by $\ttbar$. In the $\hadhad$ channel, the fake $\tauhad$ background is expected to be dominated by multijet production. However, simulation studies indicate that the contribution of $\ttbar$ events to the fake $\tauhad$ background is higher in the SR than in the CR. Therefore, an appropriate amount of simulated $\ttbar$ events with fake $\tauhad$ candidates in the CR is added to the fake $\tauhad$ template to match the fake $\tauhad$ background composition in the SR. 
In both the $\lephad$ and $\hadhad$ channels, the fake $\tauhad$ template in each SR is initially normalised to the estimated fake $\tauhad$ background yield, 
defined as the data yield minus the contributions from the simulated backgrounds with real $\tauhad$ candidates (i.e. assuming no signal contribution).
During the statistical analysis, the normalisation of the fake $\tauhad$ background in each SR is allowed to vary unconstrained in the fit to data, as discussed in Section~\ref{sec:results_Htautau}.

### 2018-09-17 sections/statistical_analysis.tex
jason comments and fix to prelim plot

The fitting procedure is initially validated through extensive studies using mocked data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 5\% are excluded (referred to as ``blinding cuts").
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions regarding some of the leading sources of uncertainty. At this point, the blinding cuts in data 
are removed and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding cuts, which are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected in the real data.

>>>>

The fitting procedure is initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 5\% are excluded (referred to as ``blinding cuts'').
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions regarding some of the leading sources of uncertainty. At this point, the blinding cuts in data 
are removed and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding cuts, which are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected in the real data.

### 2018-09-17 sections/strategy_Htautau.tex
implemented sign-off comments from George
jason comments and fix to prelim plot

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\tauhad$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\tauhad$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible tau decay products in the transverse plane. The transverse plane is transformed such that the direction of the tau decay products are 
orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$- and $y$-components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance to the $\tauhad$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\tauhad$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\tauhad$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\tauhad$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible tau decay products in the transverse plane. The transverse plane is transformed such that the direction of the tau decay products are 
orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$- and $y$-components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance to the $\tauhad$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\tauhad$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-17 sections/systematic_uncertainties.tex
jason comments and fix to prelim plot

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR". 
%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
%is applied as an uncertainty on the prediction in the nominal SR.
%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
%is applied as an uncertainty on the prediction in the nominal SR. 
%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
the relative difference in the shape of the distribution between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
is applied as an uncertainty on the prediction in the nominal SR.
In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake $\tauhad$ template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. 
The same uncertainty is assigned to the selected signal events with fake $\tauhad$ candidates.
In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\tauhad$ candidates 
between each SR and its corresponding CR in the $\ttbar$ simulation. 
Finally, the normalisation of the fake $\tauhad$ background in each SR is determined in the fit to data. 
%In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.

>>>>

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR''  and ``loose CR''. 
%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
%is applied as an uncertainty on the prediction in the nominal SR.
%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
%is applied as an uncertainty on the prediction in the nominal SR. 
%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
the relative difference in the shape of the distribution between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
is applied as an uncertainty on the prediction in the nominal SR.
In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake $\tauhad$ template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. 
The same uncertainty is assigned to the selected signal events with fake $\tauhad$ candidates.
In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\tauhad$ candidates 
between each SR and its corresponding CR in the $\ttbar$ simulation. 
Finally, the normalisation of the fake $\tauhad$ background in each SR is determined in the fit to data. 
%In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.
